manuscript

### 2022-09-15 ms/manuscript.Rmd
test references for markdown to pdf

---
title: "manuscript"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
---

# Introduction

>>>>

---
title: "manuscript"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
bibliography: refs.bib
---

# Introduction
Effects of diversity on disease exist [@ostfeld_effects_2012].
